%!TEX root = ../template.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% abstrac-en.tex
%% NOVA thesis document file
%%
%% Abstract in English([^%]*)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\typeout{NT FILE abstrac-en.tex}%

To address the tradeoffs involving scale, security and performance, together with responsiveness criteria for block-finality, new permissionless hybrid consensus models were proposed for scalable decentralized ledgers and permissionless blockchains. The hybrid consensus' core idea is based on bootstrapping efficient, scalable, and secure permissionless consensus for daily-base, combining slow or inefficient PoW (or Nakamoto inspired consensus protocols) mechanism with on-top efficient permissioned consensus, performed by dynamically formed fair committees operating under sybil-resistant sortition models. Hybrid consensus planes can use PoW consensus as a base blockchain layer, not to agree on transactions, but to agree on the sortition of committee members. Committees, in turn, can execute forms of permissioned-oriented consensus protocols for a daily-ledger blockchain layer.

In existent Hybrid Consensus approaches, the hybridization of the consensus plane is targeted to implement a specific form of sybil-resistant committee selection for a specific consensus model. In general, it is optimized for specific targeted cryptocurrency applications, not allowing other potential and diverse applications to express ways for flexible adoption of different consensus strategies, used as alternatives or used in combination.

In this dissertation we will propose the design, implementation and experimental evaluation of \mysystem: a permissionless ledger architecture supporting an hybrid and flexible consensus plane for unknown participants and operating with anti-sybil-resistance. For the expected solution the idea is to address a modular hybrid consensus service plane that can be leveraged by a base-blockchain architecture. \mysystem~will expose APIs to support transactions with on-chain smart-contracts, with the necessary expressiveness for the possible alternative or combined use of different consensus mechanisms that will be provided by the designed runtime consensus service plane.

% Palavras-chave do resumo em Inglês
% \begin{keywords}
% Keyword 1, Keyword 2, Keyword 3, Keyword 4, Keyword 5, Keyword 6, Keyword 7, Keyword 8, Keyword 9
% \end{keywords}
% \keywords{Decentralized Ledgers \and Consistent and Replicated Ledgers \and Permissionless Blockchains \and Parallel Blockchains \and Consensus \and Consensus models \and Hybrid Consensus \and Sybil Resistance \and Flexible Consensus Plane \and Flexible Consensus with Unknown Participants \and Smart Contracts \and Security \and Dependability }
\keywords{Decentralized Ledgers \and Consistent and Replicated Ledgers \and Permissionless Blockchains \and Parallel Blockchains \and Consensus models \and Hybrid and Flexible Consensus Plane \and Sybil Resistance \and Flexible Consensus with Unknown Participants \and Smart Contracts \and Security \and Dependability }
