%!TEX root = ../template.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% annex1.tex
%% NOVA thesis document file
%%
%% Chapter with example of appendix with a short dummy text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\typeout{NT FILE annex1.tex}%

\chapter{Elaboration Work Plan Activities}
\label{ann:work_plan}

The future work can be divided into $4$ main activities with a total of $11$ tasks, including the preparation of defense of the dissertation and is defined as follows:

\paragraph{Refinement of specifications and setup for prototype development}

\begin{itemize}
    \item \textbf{Task 1:} $22$/Feb/$2023$ - $08$/Mar/$2023$: Refinement of system design model and consolidation of design specification for system model components and software architecture. This includes the definition of development environment and planned micro and macro testbenches;
    
    \item \textbf{Task 2:} $01$/Mar/$2023$ - $15$/Mar/$2023$: Preparation and setup for the development environment, with the selected blockchain platform and related cloud-environment (as a Service Solution) that will be adopted for the first prototype.
\end{itemize}



\paragraph{\mysystem~Platform prototype 1 development and testing}

\begin{itemize}    
    \item \textbf{Task 3:} $15$/Mar/$2023$ - $03$/May/$2023$: Development of \mysystem~in its prototype 1 phase, planned to include the first model of hybrid multi-consensus service plane using \gls{PoW} and \gls{PBFT} based mechanisms and related sybil-resistant committee election;

    \item \textbf{Task 4:} $03$/5/$23$ - $24$/5/$23$: Support for consensus-change transactions based on verifiable smart contracts in prototype 1;

    \item \textbf{Task 5:} $03$/May/$2023$ - $31$/May/$2023$: Experimental tests and validation of \mysystem~prototype.
\end{itemize}



\paragraph{\mysystem~Platform prototype 2 (final) development and testing}

\begin{itemize}    
    \item \textbf{Task 6:} $31$/May/$2023$ - $07$/Jun/$2023$: Experimental tests and benchmark verifications related to the operation of consensus-change smart contracts in prototype 1;

    \item \textbf{Task 7:} $07$/Jun/$2023$ - $12$/Jul/$2023$: Development of \mysystem~in its prototype 2 phase, with extended support of prototype 1 to support a \gls{PoS} consensus mechanism in its consensus plane;

    \item \textbf{Task 8:} $12$/Jul/$2023$ - $04$/Aug/$2023$: Depending on the success of the plan until $19$/July, it is open a possible extension and proof-of-concept for the inclusion of a \gls{PoET} mechanism for the consensus plane of prototype 2. This is planned to be analyzed with \gls{PoET} elected/selected committees with some members running the consensus plane in isolation in a hardware-\gls{SGX}-enabled Intel Cloud node, and other members running in emulated software \gls{SGX}-virtualized nodes. In contingency, this task can be suspended;

    \item \textbf{Task 9:} $05$/Jul/$2023$ - $04$/Aug/$2023$, $25$/Aug/$2023$ - $31$/Aug/$2023$: Experimental evaluation of \mysystem~prototype 2.
\end{itemize}




\paragraph{Dissertation report writing and preparation for defense}

\begin{itemize}    
    \item \textbf{Task 10:} $08$/Mar/$2023$ - $29$/Jul/$2023$: Report writing effort, conducted in the following evolutive way:
    \begin{itemize}
        \item Chap. 1 - Introduction and Chap 2 - Background ($08$/Mar/$2023$ - $22$/Mar/$2023$);
        \item Chap. 3 - Related Work ($17$/May/$2023$ - $31$/May/$2023$);
        \item Chap. 4 - \mysystem~platform: System model and Architecture (Jun/$2023$);
        \item Chap. 5 - \mysystem~Implementation (until $15$/Jul/$2023$);
        \item Chap. 6 - Experimental evaluations and validation ($15$/Jul/$2023$ - $15$/Sep/$2023$);
        \item Chap. 7 - Conclusions and future work ($15$/Sep/$2023$ - $22$/Sep/$2023$);
        \item Final report review and delivery: $01$/Sep/$2023$ - $22$/Sep/$2023$.
    \end{itemize}

    \item \textbf{Preparation for defense:} $25$/Sep/$2023$ - $11$/Oct/$2023$: Preparation of presentation materials for the thesis defense, including presentation slides and publication of the GitHub-based prototype implementation.
\end{itemize}